\LARGE \bf Approximately Orchestrated Road Traffic Automata:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
added some of dr chius comments and responded to a few

Autonomous vehicles have seen great advancements in recent years, and such
vehicles are now ever closer to being commercially available.  The advent of
driverless cars provides opportunities for optimizing traffic in ways not
possible before. This paper introduces an open source multi-agent microscopic
traffic simulator called AORTA, which stands for \textit{Approximately
Orchestrated Road Traffic Automata}, designed for optimizing autonomous traffic
at a city-wide scale. AORTA creates scale simulations of the real world by
generating maps using publicly available road data from \textit{OpenStreetMap}
(OSM). This allows simulations to be set up through AORTA for a desired region
anywhere in the world in a matter of minutes. AORTA allows for optimizing
traffic by creating more intelligent behaviors for individual drivers (agents),
as well as by defining new intersection policies that can be followed by these
autonomous agents. These agent behaviors define how agents interact with one
another, follow intersection policies, and select the next action to take. This
paper demonstrates a simple applications using AORTA through an experiment
testing an intersection policy designed for autonomous vehicles at a city-wide
scale.

@@

Autonomous vehicle technology has made tremendous progress in the last decade.
In 2004, the farthest distance traveled by a vehicle autonomously in the DARPA
Grand Challenge was 11.9km \cite{cnnGrandChallenge2004}. By 2007, six of the
competing teams completed the 96km course set for the DARPA Urban Challenge
\cite{spectrumUrbanChallenge2007}. They did so while following the same traffic
laws followed by human drivers, navigating along with other moving vehicles,
and following correct intersection precedence order. Since then, Google's
driverless cars have clocked more than 250,000km on public roads in urban
California, USA \cite{tedThrun2011}. In 2010, researchers from the University
of Parma successfully completed an autonomous \textit{intercontinental} run
from Parma, Italy to Shanghai, China \cite{cnnVislab2010}. The successful
completion of all these milestones suggests that autonomous cars are here to
stay, and are ever closer to becoming commercially available. With the arrival
of autonomous cars, it also becomes possible to optimize traffic in ways not
possible for human drivers.

@@

This paper introduces an open source multi-agent microscopic traffic simulator
called AORTA, which stands for \textit{Approximately Orchestrated Road Traffic
Automata}, a platform designed for testing autonomous vehicle behaviors and
intersection policies. Autonomous vehicles, termed \textit{agents}, use
behaviors to interact with one another, follow intersection policies, and
decide on both long term and short term actions. AORTA allows for the creation
of intersection policies on top of a reservation based intersection manager
\cite{JAIR08-dresner}, and these policies designate when agents can cross the
intersection. AORTA's goal is to allow for the definition of new agent
behaviors and intersection policies to optimize autonomous traffic.
Additionally, by assigning human-like behaviors such as the ``car following
model'' \cite{brackstone1999car} to agents, and traffic-signal-like policies to
intersections, AORTA could potentially simulate human traffic.

Like any other microscopic traffic simulator, AORTA needs maps to run
simulations. One of AORTA's key features is that it generates maps using real
road data available from OpenStreetMap (OSM) \cite{osm}, a Wikipedia-like
interface for world maps. A map for any desired city in the world can be
downloaded, which is then parsed by AORTA to set up a scale simulation of the
real world in a few minutes. AORTA is available open-source and is easily
extensible \footnote{Code available at
\texttt{http://code.google.com/p/road-rage}} \commentpk{could also change this
to a citation}, making it easier for users to test out a number of agent
behaviors and intersection policies.

@@

Computational processing power has made excellent advancements in the last two
decades. Parallel computing and the use of GPUs have enabled microscopic models
of traffic simulation to generate results at a meaningful scale (city-wide or
greater) \cite{nagel1994microscopic,shen2011agent}. As a result, a number of
multi-agent micro-simulators have been introduced in the past decade. We review
relevant simulators and other related work in this section.

@@

Another popular open source traffic simulator that can use OSM data is SUMO
\cite{SUMO2011}, which shares the similar goals as AORTA. SUMO has been used to
study the effect of automated transportation systems, route planning of
individual vehicles, as well as dynamically adapting traffic signal policies to
increase traffic efficiency.  AORTA and SUMO differ in the manner in which
intersections are handled. SUMO uses traditional traffic signals, while AORTA
adopts a much more general \textit{reservation} system. A reservation tells a
car when it is safe to take its desired path through the intersection.
Reservations can be allotted to vehicles through more traditional means such as
traffic signals or stop-sign based intersection precedence, or through more
efficient methods designed specifically for autonomous vehicles
\cite{JAIR08-dresner}.

@@

\commentpk{I remember you guys mentioning there was a paper for SUMO describing
a similar process, we should ref it as to why OSM data is not directly suitable}

@@

A map is represented as a directed graph with \emph{lanes} as edges and
\emph{turns} as vertices. A \emph{road} groups a set of lanes together, one set
for each direction of travel. \emph{Intersections} map the possible turns from
incoming to outgoing lanes.  Since both lanes and turns support traffic, they
are grouped together as \emph{traversables}, meaning agents may exist on them.
\commentc{What about parking lots?}

The map also has a geometric interpretation, used for visualization and
measuring physical distances. A road contains a sequence of points, defining
the center line that divides the road into two directions of travel. AORTA
interprets these points as straight lines and projects parallel lanes out using
a fixed width. Turns are modeled with a single straight line connecting the end
of one lane to the start of another. \commentc{Illustrate through a figure?}

@@

Different elements of the simulator are described as follows:

@@

AORTA uses microscopic simulation, modeling individual drivers as point agents
following a simple acceleration-based dynamics model \commentpk{need ideas on
framing the last sentence better}.  Time is modeled discretely, and an
agent accelerates at a fixed rate for the duration of a ``step'' to achieve a
new position and velocity. Space is continuous, meaning agents occupy a moving
interval of a lane, rather than one fixed tile of the road. Each time step
lasts for the same fixed duration, and the simulation does the following after
each time step:

@@

@@

However, with very high volumes of traffic, it is possible for waiting agents to
accumulate and fill lanes to their capacity. When this happens in a circular
manner so that the agent at the front of each lane is waiting to perform a turn
into another full lane with the same such head agent, gridlock \cite{gridlock}
occurs; no agent in the system will make progress unless an agent at the front
decides to pick a different turn. Figure \ref{fig:gridlock} demonstrates this.
AORTA can detect this by finding cycles in the graph of the ``is following''
relation.

@@

In many observed cases, the gridlock is caused by AORTA's present lack of
lane-changing support: agents loop around these intersections in order to enter
a lane adjacent to their original lane. Since these routes are still legal, it
is desirable to prevent or mend this without forcing different routes. The
conditions under which every vehicle eventually may proceed are known.
\cite{AAAI11-au}.

@@

There are three main components of the simulation, each configurable by
extending built-in implementations of an interface: agent behaviors, routing
strategies, and intersection policies.

@@

Intersection policies are one of the most intriguing aspects of the simulation
to tweak, especially in light of autonomous vehicles. Current policies include
traditional stop signs, traffic signals, and an AIM-inspired autonomous
reservation system \cite{JAIR08-dresner}. The traffic signals are further
extensible by assigning groups of non-conflicting turns at each intersection
with some duration and offset. Future policies could include signals that adapt
timings and refinements to the autonomous reservation policy.

To pick turns, agent behaviors consult a route strategy. Two simple
implementations exist already: a static route using A* \cite{astar} and a
drunken walk that probabilistically moves towards the destination.  Researchers
can experiment with dynamic replanning or hierarchial planning without modifying
any code other than creating a new route implementation. Route policies could
also interact with a singleton overseer to gain some sort of global insight or
with smart intersections to avoid congestion.

@@

A particular focus of AORTA is intersection policies. To demonstrate how much
policy affects agent performance \commentd{performance is a vague term, but I
don't want to talk about dependent vars just yet}, three policies are evaluated: stop sign,
traffic signal, and autonomous reservation.

@@

The experiment simulates a 6 by 7 mile slice of downtown Austin,
Texas\footnote{bounded by the Mopac and Springdale Road horizontally, and Oltorf
Street and Koenig Lane vertically}, for one hour. The step duration is fixed at
0.1 seconds. While the intersection policies vary, the agents spawned and their
routes remain the same. A generator creates one new agent every 1 simulation
second, with a uniformly random starting position and goal.

@@

Stop signs accept agents FCFS, refusing agents until they have idled at 0 speed
for 1 second. This delay approximates human reaction time.

The traffic signal policy requires timings and groups of simultaneous turns for
each intersection. The heuristic evaluated uses standard turn groups (turns from
parallel incoming directions are scheduled simultaneously, and left turns are
grouped) and employs breadth-first search to propagate timings. The goal is to
synchronize green signals so agents in some lanes do not stop for several
intersections.

\commentd{advice on wording?}
Finally, in anticipation of the advent of autonomous vehicles, an autonomous
reservation policy inspired by AIM \cite{JAIR08-dresner} is tested. This policy
allows new agents to join existing groups of agents if their turn is compatible
with the others. To prevent one heavy direction of traffic from hogging the
intersection indefinitely, a timeout preemptively cycles through reservations.
Ideally this should be based on the relative numbers of agents depending on
their group of reservations. \commentd{take out the last sentence? all of the
policies could use some work.}

@@

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{avg_lag_agent_atx.png}
  \caption{The distribution of average delay reveals that traffic signals can
           cause the most lag.}
  \label{fig:avg_lag}
  \vspace{-10pt}
\end{figure}

If an intersection immediately permits an agent to proceed and grants other
agents in the same lane similar access (because this new agent must still follow
these others), then the new agent may simply proceed at full speed limit without
pausing. This gives the least possible delay spent along some lane, so any extra
time is defined as lag and is used to measure intersection performance. Figure
\ref{fig:avg_lag} graphs the average of this delay per agent. On average,
reservation policies cause less than 1 second of delay at each intersection,
stop signs cause about 7 seconds lag, and traffic signals cause 16 seconds.

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{agent_cnt_atx.png}
  \caption{Autonomous reservations outperform stop signs, and traffic signal
           gridlocked.}
  \label{fig:agent_cnt}
  \vspace{-10pt}
\end{figure}

The number of agents changes because the continuous generator introduces a new
agent every second. This count reaches a steady state when the generator
introduces an agent at the same rate as older agents finish their route. Figure
\ref{fig:agent_cnt} reveals that autonomous reservations let agents reach their
destination twice as quickly as the competition, with a steady-state of about
400 agents. The count for traffic signals continues to increase because gridlock
occurred in one segment of the map, causing agents to not finish their route.
Unexpected starvation was also observed: although the signals cycle through
turns regularly, agents cannot proceed when the previous cycle caused a
destination lane to fill and become blocked.

Each policy has its trade-offs in terms of performance and physical hardware
cost \commentd{do we want to raise this issue?}, suggesting a mixed approach,
perhaps with intersection policies adapting as traffic conditions shift.
Researchers could conduct this experiment and many others without needing to
understand most of AORTA's code-base. The largest intersection policy, traffic
signals with the flooding heuristic for timing assignment, is only 400 lines of
Scala.

@@

AORTA's map construction process, although flexible, is fraught with heuristics,
motivating proposed changes to OSM. Road type annotations imprecisely estimate
the number of lanes and typical speed limits, resulting in incorrect graphs.
Guessing the turns at each intersection makes common road features like right
turn-only lanes and shared center left turn lanes hard to detect. There are many
circumstances where AORTA simulates one intersection as several in close
proximity because roads do not geometrically line up, but semantically they do.
If OSM could encode this, the performance of intersection policies such as
traffic signals would vastly improve in those regions. Other simulators have
identified similar issues before \cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.

>>>>

Autonomous vehicles have seen great advancements in recent years, and such
vehicles are now ever closer to being commercially available.  The advent of
driverless cars provides opportunities for optimizing traffic in ways not
possible before. This paper introduces an open source multiagent microscopic
traffic simulator called AORTA, which stands for \textit{Approximately
Orchestrated Road Traffic Automata}, designed for optimizing autonomous traffic
at a city-wide scale. AORTA creates scale simulations of the real world by
generating maps using publicly available road data from \textit{OpenStreetMap}
(OSM). This allows simulations to be set up through AORTA for a desired region
anywhere in the world in a matter of minutes. AORTA allows for optimizing
traffic by creating more intelligent behaviors for individual drivers (agents),
as well as by defining new intersection policies that can be followed by these
autonomous agents. These agent behaviors define how agents interact with one
another, follow intersection policies, and select the next action to take. This
paper demonstrates a simple applications using AORTA through an experiment
testing an intersection policy designed for autonomous vehicles at a city-wide
scale.

@@

Autonomous vehicle technology has made tremendous progress in the last decade.
In 2004, the farthest distance traveled by a vehicle autonomously in the DARPA
Grand Challenge was 11.9km \cite{cnnGrandChallenge2004}. By 2007, six of the
competing teams completed the 96km course set for the DARPA Urban Challenge
\cite{spectrumUrbanChallenge2007}. They did so while following the same traffic
laws followed by human drivers, navigating along with other moving vehicles,
and following correct intersection precedence order. Since then, Google's
driverless cars have clocked more than 250,000km on public roads in urban
California, USA \cite{tedThrun2011}. In 2010, researchers from the University
of Parma successfully completed an autonomous \textit{intercontinental} run
from Parma, Italy to Shanghai, China \cite{cnnVislab2010}. The successful
completion of all these milestones suggests that autonomous cars are here to
stay, and are ever closer to becoming commercially available. With the arrival
of autonomous cars, it also becomes possible to optimize traffic in ways not
possible for human drivers. 
\commentd{If we need space, I agree with Dr Chiu, some of this could be trimmed}

@@

This paper introduces an open source multigent microscopic traffic simulator
called AORTA, which stands for \textit{Approximately Orchestrated Road Traffic
Automata}, a platform designed for testing autonomous vehicle behaviors and
intersection policies. Autonomous vehicles, termed agents, use
behaviors to interact with one another, follow intersection policies, and
decide on both long term and short term actions. AORTA allows for the creation
of intersection policies that designate when agents can cross the
intersection. AORTA's goal is to allow for the definition of new agent
behaviors and intersection policies to optimize autonomous traffic.
Additionally, by assigning human-like behaviors such as the ``car following
model'' \cite{brackstone1999car} to agents, and traffic-signal-like policies to
intersections, AORTA could potentially simulate human traffic.
\commentd{Previously, ``AORTA allows for the creation
of intersection policies on top of a reservation based intersection manager
\cite{JAIR08-dresner}, and these policies designate when agents can cross the
intersection.'' Actually, reservations are just one policy. Do we want to focus
on the general case here, or autonomous specifically?}

Like any other microscopic traffic simulator, AORTA needs maps to run
simulations. One of AORTA's key features is that it generates maps using real
road data available from OpenStreetMap (OSM) \cite{osm}, a moderated,
user-editable interface for world maps. A map for any desired city in the world
can be downloaded, which is then parsed by AORTA to set up a scale simulation of
the real world in a few minutes. AORTA is available open-source and is easily
extensible \footnote{Code available at
\texttt{http://code.google.com/p/road-rage}} \commentpk{could also change this
to a citation}, making it easier for users to test out a number of agent
behaviors and intersection policies.

@@

Computational processing power has made excellent advancements in the last two
decades. Parallel computing and the use of GPUs have enabled microscopic models
of traffic simulation to generate results at a meaningful scale (city-wide or
greater) \cite{nagel1994microscopic,shen2011agent}. As a result, a number of
multiagent micro-simulators have been introduced in the past decade. We review
relevant simulators and other related work in this section.

@@

Another popular open source traffic simulator that can use OSM data is SUMO
\cite{SUMO2011}, which shares the similar goals as AORTA. SUMO has been used to
study the effect of automated transportation systems, route planning of
individual vehicles, as well as dynamically adapting traffic signal policies to
increase traffic efficiency.  AORTA and SUMO differ in the manner in which
intersections are handled. SUMO uses traditional traffic signals, while AORTA
adopts a much more general \textit{reservation} system. A reservation tells a
car when it is safe to take its desired path through the intersection.
Reservations can be allotted to vehicles through more traditional means such as
traffic signals or stop-sign based intersection precedence, or through more
efficient methods designed specifically for autonomous vehicles
\cite{JAIR08-dresner}.
\commentd{Again, ``reservation'' feels like an overloaded term here, meaning the
general notion of being able to cross, as opposed to the specific policy.}

@@

\commentpk{I remember you guys mentioning there was a paper for SUMO describing
a similar process, we should ref it as to why OSM data is not directly suitable}
\commentd{We cite it in the conclusion because they had similar critiques about
  OSM. I don't think we have a source for why OSM isn't directly suitable,
  although that source also describes a conversion process.}

@@

A map is represented as a directed graph with \emph{lanes} as edges and
\emph{turns} as vertices. A \emph{road} groups a set of lanes together, one set
for each direction of travel. \emph{Intersections} map the possible turns from
incoming to outgoing lanes.  Since both lanes and turns support traffic, they
are grouped together as \emph{traversables}, meaning agents may exist on them.
\commentc{What about parking lots?}
\commentd{They're not something relevant for us to model. I don't think we need
to mention this.}

The map also has a geometric interpretation, used for visualization and
measuring physical distances. A road contains a sequence of points, defining
the center line that divides the road into two directions of travel. AORTA
interprets these points as straight lines and projects parallel lanes out using
a fixed width. Turns are modeled with a single straight line connecting the end
of one lane to the start of another. \commentc{Illustrate through a figure?}
\commentd{maybe a subfloat by the turn conflicts, sure}

@@

\commentd{Is this incomplete?}
Different elements of the simulator are described as follows:

@@

AORTA uses microscopic simulation, modeling individual drivers as point agents
with a simple acceleration-based dynamics model. Time is modeled discretely,
and an agent accelerates at a fixed rate for the duration of a ``step'' to
achieve a new position and velocity. Space is continuous, meaning agents occupy
a moving interval of a lane, rather than one fixed tile of the road. Each time
step lasts for the same fixed duration, and the simulation does the following
for each time step:

@@

\commentd{Mike, I left off here.}

@@

However, with very high volumes of traffic, it is possible for waiting agents to
accumulate and fill lanes to their capacity. When this happens in a circular
manner so that the agent at the front of each lane is waiting to perform a turn
into another full lane with the same such head agent, gridlock \cite{AAAI11-au}
occurs; no agent in the system will make progress unless an agent at the front
decides to pick a different turn. Figure \ref{fig:gridlock} demonstrates this.
AORTA can detect this by finding cycles in the graph of the ``is following''
relation.

@@

In many observed cases, the gridlock is caused by AORTA's present lack of
lane-changing support: agents loop around these intersections in order to enter
a lane adjacent to their original lane. Since these routes are still legal, it
is desirable to prevent or mend this without forcing different routes. However,
choosing alternative moves (by changing lanes or rerouting) is one sufficient,
but not necessarily required, condition for liveness \cite{AAAI11-au}.
\commentd{I misinterpreted the results of the paper originally. Is this a safer
and more relevant claim to make?}

@@

There are three main configurable components of the simulation, each with at
least one existing implementation: agent behaviors, routing strategies, and
intersection policies.

@@

Intersection policies are one of the most interesting aspects of the simulation
to tweak, especially in light of autonomous vehicles. Current policies include
traditional stop signs, traffic signals, and an AIM-inspired autonomous
reservation system \cite{JAIR08-dresner}. The traffic signals are further
extensible by assigning groups of non-conflicting turns at each intersection
with some duration and offset. Future policies could include signals that adapt
timings and refinements to the autonomous reservation policy.
\commentc{You can mention about using optimized traffic signal timings generated
  by commercial traffic signal optimization packages such as SYNCHRO (cite
  Husch, D. and Albeck, J. (2004) Trafficware Synchro 6 User Guide, TrafficWare,
  Albany, California.)
}

To pick turns, agent behaviors consult a route strategy. Two simple
implementations exist already: a static route using A* \cite{astar} and a
drunken walk that probabilistically moves towards the destination.  Researchers
can experiment with dynamic replanning or hierarchial planning without modifying
any code other than creating a new route implementation. Route policies could
also interact with a single central manager to gain some sort of global insight or
with autonomous intersections to avoid congestion.
\commentd{I can cite a paper for hierarchial planning. As for why, the 2
  mentioned are just examples of future work we intend to do, and I want to make
  the point that implementing both would be easy from a software engineering
  perspective.}

@@

A particular focus of AORTA is intersection policies. To demonstrate how much
policy affects the throughput of intersections and total performance of the
transportation system, three policies are evaluated: stop sign, traffic signal,
and autonomous reservation. Every intersection uses the same policy.

@@

The experiment simulates a 6 by 7 mile slice of downtown Austin,
Texas\footnote{bounded by the Mopac and Springdale Road horizontally, and Oltorf
Street and Koenig Lane vertically}, for one hour. The step duration is fixed at
0.1 seconds. While the intersection policies vary, the agents spawned and their
routes remain the same. A generator creates one new agent every 1 simulation
second, with a uniformly random starting position and goal.
\commentd{Chiu asked about the distribution of incoming agents. Is ``uniformly
random start and end'' not clear?}

@@

Stop signs accept agents first-come, first-served, refusing agents until they
have idled at 0 speed for 1 second. This delay approximates human reaction time.

The traffic signal policy requires timings and groups of simultaneous turns for
each intersection. The heuristic evaluated uses standard turn groups (turns from
parallel incoming directions are scheduled simultaneously, and left turns are
grouped) and employs breadth-first search to propagate timings. The goal is to
synchronize green signals so agents in some lanes do not stop for several
intersections.
\commentd{chiu recommends more details with how we propagate timings. Thoughts,
Mike?}

\commentd{advice on wording?}
Finally, in anticipation of the advent of autonomous vehicles, an autonomous
reservation policy inspired by AIM \cite{JAIR08-dresner} is tested. This policy
groups agents with compatible turns together, allowing new agents to join
existing groups. To prevent one heavy direction of traffic from hogging the
intersection indefinitely, a timeout preemptively cycles through reservations.

@@

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{avg_lag_agent_atx.png}
  \caption{The distribution of average delay reveals that traffic signals can
           cause the most lag.}
  \label{fig:avg_lag}
  \vspace{-10pt}
\end{figure}
\commentc{This figure only shows the distributions for a particular
  traffic level only. People would wonder what is the traffic level.
Actually people are more interested to see how it varies with
different traffic levels so a few more graphs like this at
different traffic level is helpful.}
\commentc{Remove ``In this range'' in the y-label.}
\commentc{Replace ``lag'' with ``delay'' in the x-label}}

If an intersection immediately permits an agent to proceed and grants other
agents in the same lane similar access (because this new agent must still follow
these others), then the new agent may simply proceed at full speed limit without
pausing. This gives the least possible delay spent along some lane, so any extra
time is defined as lag and is used to measure intersection performance. Figure
\ref{fig:avg_lag} graphs the average of this delay per agent. On average,
reservation policies cause less than 1 second of delay at each intersection,
stop signs cause about 7 seconds lag, and traffic signals cause 16 seconds.
\commentd{We need to be clear that our traffic lights suck, so this number is
pretty biased.}

\commentc{Reviewers will certainly complain the lack of the details of the
  parameters you used, which implies your results can be somewhat ``biased''.
  Honestly, I don't think you should show this results in
  this paper because it is somewhere irrelevant to the topic.  Perhaps
  you should emphasize that these experiments intend to show what you can do
with your simulator.
}

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{agent_cnt_atx.png}
  \caption{Autonomous reservations outperform stop signs, and traffic signal
           gridlocked. \commentc{This label is not helpful. Clarify ``active'' in y label.}}
  \label{fig:agent_cnt}
  \vspace{-10pt}
\end{figure}

The number of agents driving at some time changes because the continuous
generator introduces a new agent every second. This count reaches a steady
state when the generator introduces an agent at the same rate as older agents
finish their route. Figure \ref{fig:agent_cnt} reveals that autonomous
reservations let agents reach their destination twice as quickly as the
competition, with a steady-state of about 400 agents. The count for traffic
signals continues to increase because gridlock occurred in one segment of the
map, causing agents to not finish their route.  Unexpected starvation was also
observed: although the signals cycle through turns regularly, agents cannot
proceed when the previous cycle caused a destination lane to fill and become
blocked.

Each policy has its trade-offs in terms of performance and physical hardware
cost \commentd{do we want to raise this issue?}, suggesting an approach that
controls different intersections with different polices, perhaps adapting
policies adapting as traffic conditions shift.  Researchers could conduct this
experiment and many others without needing to understand most of AORTA's
code-base. The largest intersection policy, traffic signals with the flooding
heuristic for timing assignment, is only 400 lines of code in Scala.

@@

AORTA's map construction process, although flexible, cannot completely account
for incompletedness in OSM data.  Road type annotations imprecisely estimate
the number of lanes and typical speed limits, resulting in incorrect graphs.
Guessing the turns at each intersection makes common road features like right
turn-only lanes and shared center left turn lanes hard to detect. There are
many circumstances where AORTA simulates one intersection as several in close
proximity because roads do not geometrically line up, but semantically they do.
If OSM could encode this, the performance of intersection policies such as
traffic signals would vastly improve in those regions. Other simulators have
identified similar issues before \cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.
